---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Landscape-and-Challenges

<!-- badges: start -->
<!-- badges: end -->


```{r,echo=FALSE}
#--Load library WDI---#
library(WDI)

#-- Get indicator population total ---#
listCountry <- c("US","IN", "CN") 
variable <- "NY.GDP.MKTP.KD.ZG" 

#--- Choose recent year ----#
startYear <- 1990
endYear <- as.numeric(format(Sys.time(), '%Y'))

#---- Build dataframe ---#
dataInput <- WDI(indicator = variable, country = listCountry, start = startYear, end = endYear)

colnames(dataInput)[which(colnames(dataInput)==variable)] <- "indicator"

dataInput$country <- as.factor(dataInput$country)

names(dataInput)[names(dataInput) == "country"] <- "Pays"

dataInput <- na.omit(dataInput)

library(ggplot2)
library(RColorBrewer)
ggplot(data=dataInput, aes(x=year, y=indicator, group=Pays)) +
  geom_line(aes(linetype=Pays), color="black")+
  xlab("") + 
  ylab("") +
  ggtitle("") +
  theme_void() + 
  theme(legend.position="none")
```


This course presents an integrated overview of international business environment and its related issues.

There are five key objectives for the course:

- Understand the international competitive environment in which firms operate
- Understand the origins, development, and consequences of globalization for economic and financial activities of nation states and firms
- Analyze national and international policies with regard to globalization, trade and growth
- Develop an understanding of the business and economic environment of prominent emerging markets
- Provide students with theoretical and analytical international business frameworks, which they maychoose to use in their Master’s thesis or supervised project

## Data

For each session, you will find a csv file allowing you to complete the data challenge.

### Contact information

Thierry Warin
Full Professor 
Email: thierry.warin@hec.ca
[[HEC]](https://www.hec.ca/en/profs/thierry.warin.html){target="_blank"}
